Bird beak's elaboration and innovation

### 2022-07-19 Analysis/03-Elaboration_innovation_analysis.Rmd
Update 03-Elaboration_innovation_analysis.Rmd

```{r, eval = FALSE, echo = FALSE}
## General measurement
super_orders_stats <- ellipse.stats(superorder_shapespace)
orders_stats <- ellipse.stats(order_shapespace)
suborder_stats <- ellipse.stats(suborder_shapespace)
family_stats <- ellipse.stats(family_shapespace)

>>>>

```{r, eval = FALSE, echo = FALSE}
source("../Functions/stats.utilities.R")
## General measurement
super_orders_stats <- ellipse.stats(superorder_shapespace)
orders_stats <- ellipse.stats(order_shapespace)
suborder_stats <- ellipse.stats(suborder_shapespace)
family_stats <- ellipse.stats(family_shapespace)
